---
title: "mengfany_week1"
author: "Mengfan YU"
date: "2022-11-03"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### There are some packages that we should install at first.

```{r}
options(repos = list(CRAN="http://cran.rstudio.com/"))
install.packages("sf")
install.packages("ggplot2")
install.packages("tidyverse")

```

Then, use these packages.

```{r}
library(ggplot2)
library(sf)
library(tidyverse)

```

## `ggplot` and `geom_sf` function

The first map shows the topology of Moutain Parks of Boulder Colorado by using `topo.colors()`. The blue area means low elevation, while the yellow means high elevation.

In the second map, I used the `ifelse()` function to present the area where the distance to streets and parking lots is less than 50 meters. This map indicates the areas where human activities are active.


```{r}

boulder <- st_read("M:/geoviz/week1/Boulder_Data/BoulderSocialMedia.shp")
boulder = st_transform (boulder, 26753) 

ggplot() +
    geom_sf(data =boulder, aes(color=PT_Elev),
    fill = NA, alpha = .2) +
  scale_colour_gradientn(colours = topo.colors(12)) +  
  theme_bw()


library(dplyr)

boulder %>%
    mutate(street_buffer = ifelse(Street_dis <= 50, TRUE, FALSE))%>% 
ggplot() +
  geom_sf(aes(color=street_buffer),
    fill = NA, alpha = .2)  +  
  theme_bw()


```



## Boxplot 
```{r}

boulder %>%
  filter(DB ==  'Pano' | DB == 'Flickr') %>%
  ggplot(aes(x=DB, y=Hydro_dis)) + 
  geom_boxplot()

```
The Y axis represents the distance to lakes, rivers, and creeks, and the X axis represents the photos posted by people that come from social media "Flickr" or "Pano". 

As we can see in the chart,  comparing the mean distance of these photographs from the nearest water body, the distance to lakes and other water body has a significant relationship with photographs on social media. The mean value is about 1600 meters, which means people take pictures at a distance of 1600 meters from the water body. 


## tmap

```{r}

install.packages("tmap")

```

Using `tmap` to make an interactive map

```{r}

library(tmap)
tmap_mode("view")

## Add the data - these are specific to the vector or raster
tm_shape(boulder) + 
  ## which variable, is there a class interval, palette, and other options
  tm_symbols(col='PT_Elev',
             style='quantile',
             palette = 'YlOrRd',
             border.lwd = NA,
             size = 0.1,
             title.size="Elevation in Boulder Colorado",
        title.col="Elevation (meters)"
  )

```

The end.
